### 2020-10-15 priority-gv.tex
Handled one of Simon's worries.

Configurations are typed by a judgement $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$, which states that ``a configuration $\tm{\conf{C}}$ with flag $\phi$ is well-typed under typing environment $\ty{\Gamma}$''\simon{I found it surprising that configuration typing doesn't need priority annotations. Can you give an intuitition why?}. Configuration typing is based on the standard typing for GV. Terms are embedded either as main or as child threads. The priority bound from the term typing is discarded, as configurations contain no further sequential actions. Main threads are allowed to return a value, whereas child threads are required to return the unit value. Sequents are annotated with a flag $\phi$, which ensure that there is at most one main thread.

>>>>

Configurations are typed by a judgement $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$, which states that ``a configuration $\tm{\conf{C}}$ with flag $\phi$ is well-typed under typing environment $\ty{\Gamma}$''. Configuration typing is based on the standard typing for GV. Terms are embedded either as main or as child threads. The priority bound from the term typing is discarded, as configurations contain no further blocking actions. Main threads are allowed to return a value, whereas child threads are required to return the unit value. Sequents are annotated with a flag $\phi$, which ensure that there is at most one main thread.
